My title

### 2024-03-11 paper/paper.qmd
region discussion

Combing figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time. The estimates are significant if the intervals do not cross 0. The value for the estimates are in log-odds, indicating that if the interval is positive, the individual supports Biden, if negative, the individual supports Trump.

@@

@@

We observe

@@

>>>>

Combing figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time. The estimates are significant if the intervals do not cross 0. The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.

@@

maybe talk about race?

@@

Our analysis highlights regional voting variations, with the Northeast, West, and Midwest favoring Biden, while the South supports Trump. These differences stem from diverse cultural, family, religious, and social perspectives.

Biden's support base is concentrated in the Mid-Atlantic states, New England, the West Coast, Southwestern states, and certain regions around the Great Lakes. This support is particularly evident in notable cities within these regions, driven by various factors including liberal ideals and progressive policies. For instance, states like New York and Massachusetts support Biden due to their liberal-leaning populations, diverse demographics, and emphasis on social justices. Similarly, on the West Coast, states such as California and Washington are known for their progressive values and advocacy for issues like environmental conservation and LGBTQ+ rights, contributing to Biden's popularity in these areas. In the Southwest, states like Arizona and Nevada, with growing minority populations and concerns over immigration policies, also show significant support for Biden. Additionally, states around the Great Lakes, including Illinois and Michigan, align with Biden's platform due to their industrial heritage and strong labor unions.

Voters favoring Biden are predominantly concentrated in big cities and large suburban regions, whereas Trump supporters are dispersed across rural areas with lower population density. Consequently, Trump secured victories in 2,588 counties, whereas Biden won over just 551 [@frey_2021]. Even in traditionally Republican states, major urban areas exhibit significant support for Biden. Notable examples include Charlotte, North Carolina; Salt Lake City, Utah; and Nashville and Memphis, Tennessee, among others [@cnn_2020].

This trend reflects the impact of diverse demographics, progressive ideologies, and evolving societal norms in urban areas. Here, a mix of cultural diversity, acceptance of progressive values, and socio-economic factors favors Biden's platform. Additionally, urban centers, with their concentration of educational and cultural institutions, often align with Democratic policies on healthcare, climate change, and social justice.

The 2020 election witnessed intriguing shifts in traditionally conservative states, turning them into battlegrounds. For instance, Texas, a Republican stronghold, saw unprecedented Democratic gains, though ultimately remaining red. Notably, the five largest cities in Texas—Houston, San Antonio, Dallas, Austin, and Fort Worth—all backed the Democratic party, marking a significant departure from historical voting patterns [@texas2020]. Similarly, Georgia, a Republican stronghold since 1992, voted for the Democratic party, reflecting evolving demographic and ideological shifts [@georgia2020].

Southern states, such as Alabama, Mississippi, and South Carolina with a large amount of Christian population, strongly adhere to conservative principles. For example, these states have implemented strict anti-abortion law and advocated for tight immigration policies. Furthermore, these states have historically been less supportive of LGBTQ+ rights. As a result, voters in these Southern states typically align with the Republican party represented by Trump, which prioritizes pro-life initiatives and traditional Christian values.

@@

maybe talk about employment?

## Talk about mail-in ballots AND Trump's later reaction to losing
